\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}

\title{Learn Computer Science}
\author{harshv}
\date{March 2023}

\begin{document}

\maketitle

\section*{Motivation}
To me it is now clear that Computer Science is the science of creating artificial
intelligence to solve problems that humans care about. As an example,
consider Amazon, the so-called "Tech Giant" which hires hundreds if not thousands 
of software engineers every year. Before Amazon existed, people were forced to
physically visit several different stores to find the items they wanted to buy.
Moreover, it was challenging to have items delivered to your door-step. 
Amazon is nothing but an artificial intelligence(running on computers) that
interacts with its customers using the Web, allowing them to search for, buy,
and get their products deliverd. In fact, every piece of code you will write
is a type of artificial intelligence which does something useful for you.
Your job as a computer science student is to learn how to specify 
artificial intelligence(in the form of code) that could solve important problems.

\section*{How to learn}
I recommend the \href{https://www.udacity.com/course/intro-to-programming-nanodegree--nd000}{Introduction To Programming} 
nanodegree by Udacity. I like it because, in my experience, the courses on Udacity are high quality,
with both good theory and hands-on projects. Moreover, you will also 
earn a certificate at the end. If you spend 8 hours every day, you should be able to finish
the course in a month, which will cost you a total of \$529 dollars using Pay-As-You-Go pricing.
Having to pay money can act as a motivating factor to work harder. Think of this expense
as an investment, not sunk cost.
\end{document}
